Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-01 07-opq-mauka.tex
checkpoint

>>>>

Figure \ref{fig:mauka-data-model} illustrates the hierarchical data model for OPQ Mauka. This data model can be conceptualized as a multi-level hierarchy that adaptively optimizes data storage using a tiered TTL approach and provides a mechanism in which typed aggregated data is continually refined to the point of being of becoming actionable. The data model also includes software components called "actors" that both move data upward through the levels and apply optimizations downward through the levels. Actors are implemented through a plugin architecture, making it easy to experiment with the data model and improve it over time.

\begin{figure}
\center \includegraphics[width=4in]{images/mauka/mauka-data-model.png}
\caption{Mauka data model hierarchy}
\label{fig:mauka-data-model}
\end{figure}

OPQ Mauka sits between OPQ Makai and OPQ’s database. It receives messages from OPQ Makai when it has triggered OPQ Boxes due to something interesting in the low-fidelity data stream. OPQ Mauka then retrieves the raw waveforms stored in the database by OPQ Makai, performs feature extraction, and then forwards the features and/or raw waveform to OPQ Mauka Actors to perform classification and other high level analytics. These results are then stored in the database. Finally, TTL Actors run at predetermined intervals to remove data whose time-to-live has expired.

\subsection{OPQ Mauka Actors}

The current capabilities of OPQ Mauka can be summarized in terms of its Actors, which are implemented as plugins.

{\em BasePlugin.} All Actor plugins derive from the BasePlugin, which provides primitives for running plugins as separate processes, serialization and deserialization of type safe messages, communication over ZeroMQ, metrics collection, MongoDB communication, debugging, and plugin health.

{\em MakaiEventPlugin.} The MakaiEventPlugin Actor is responsible for reading Events newly created by OPQ Makai into OPQ Mauka. It performs feature extraction on the raw Event data streams and forwards those features (or the raw data) to subscribing plugins. This allows OPQ Mauka to perform feature extraction once, and reuse those features in multiple plugins.

{\em FrequencyVariationPlugin.} The FrequencyVariationPlugin is used to classify generic fre- quency sags, swells, and interruptions as defined by the IEEE1159 standard[29]. Both duration and deviation from nominal are used to perform these classifications. Duration classifications in- clude frequency deviations that last for less than 50 ns, between 50 ns to 1 ms, and 1 ms to 50 ms. Classifications for deviations from nominal are performed for values that are up to 40% deviation
     49

     nominal. The plugin subscribes to messages from the “WindowedFrequency” topic which includes a payload of frequency features over one electrical cycle.
     When a message is received, the plugin uses configurable thresholds to find frequency fluctu- ations within the windowed frequency streams. The plugin is able to classify frequency swells, frequency interruptions, and frequency sags. When a new frequency variation is detected, a fre- quency Incident is created
